Printer ballistics through character's texture analysis

### 2013-11-19 Printer_Ballistics.tex
mais edição...

%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In August of 2013, a russian man wrote his own small print in a credit card contract~\cite{RT}. The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the document. The changes included unlimited credit line, 0 percent interest rates and no fees. When the bank decided to terminate the man's credit card, because overdue payments, he sued them for more than 24 million rubles (US\$ 727.000). How could the bank prove the falsification?

@@

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State-of-the-Art}
Related work: \cite{Bulan}

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Solution}

@@

\subsection{Printers dataset}

@@

\subsection{Characters}

@@

Were not considered characters from misaligned documents, i.e. characters from apparently obliquely scanned documents.

\subsection{Printers}

@@

>>>>

%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

In August of 2013, a russian man wrote his own small print in a credit card contract~\cite{RT}. The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the document. The changes included unlimited credit line, 0 percent interest rates and no fees. When the bank decided to terminate the man's credit card, because overdue payments, he sued them for more than 24 million rubles (US\$ 727.000). How could the bank prove the falsification?

@@

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State-of-the-Art}
\label{sec:state_of_the_art}

Related work: \cite{Bulan}

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Solution}
\label{sec:proposed_solution}

@@

\subsection{Printers dataset}
\label{subsec:printers_dataset}

@@

\subsection{Characters}
\label{subsec:characters}

@@

Were not considered characters from misaligned documents, i.e. characters from apparently obliquely scanned documents. Figure \ref{fig:characters} shows examples of two characters obtained from scanned documents, one of them being usable and the other not, being considered rotated.

\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{characters}
	\caption{Examples of characters: the left one was considered useful; the right one, slightly rotated.}
\label{fig:characters}   
\end{center} 
\end{figure}

Subsection \ref{subsec:co-occurence_matrix} will be explained in more detail why not use rotated characters.

\subsection{Printers}
\label{subsec:printers}

@@

\subsection{Gray level co-occurence matrix}
\label{subsec:co-occurence_matrix}

Co-occurrence matrix is a tabulation of how many different combinations of intensity values of pixels (grayscale) occur in an image. The primary use of the co-occurrence matrix is characterized texture in an image from a set of statistics for instances of
each gray level in different pixels along different directions~\cite{Rocha}.

Co-occurrence matrix considers the relationship between two pixels at a time, one called as ''reference pixel'' and another as ''neighbor pixel''. The neighboring pixel chosen can be neighbor in any direction: east (right), west (left), north (above), south (below), or diagonally, i.e. northeast, northwest, southwest and southeast of each reference pixel. Also the neighborhood need not be exactly one pixel, can be 2, 3, or any value. Each pixel within the image becomes the reference pixel, starting at the top left and proceeding to the lower right. There will be particular cases. For instance, pixels of the right margin of the image does not have neighboring right.

Co-occurrence, in its most general form, can be specified by a matrix of relative frequencies $P (i, j, d,\theta)$, where two neighboring texture elements separated by a distance $d$ in a direction $\theta$ occur in the image, one with the property $i$ and another with property $j$.

From a co-occurrence matrix can be obtained some properties of the analyzed image. For this work, we used the properties of contrast, correlation, energy and homogeneity to create a fingerprint of the printed characters.

Using an example similar to the rotated character, we can compare the value differences in the properties obtained from the co-occurrence matrix (Figure \ref{fig:characters_angle}). In this case, the character on the left was obtained directly from the scanned document, the character on the right is the same character, but rotated -4º.

\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{characters_angle}
	\caption{On the left, a character obtained from a scanned document and to the right, the same character, rotated -4º.}
\label{fig:characters_angle}   
\end{center} 
\end{figure}

Table \ref{tab:properties_differences} lists the differences between the properties of the character sample obtained from the co-occurrence matrix.

\begin{table}
\label{tab:properties_differences}
\caption{Differences between an original character and a rotated character.}
\begin{center}
\begin{tabular}{l*{3}{c}r}
Property & Original character & Rotated character (-4º) \\
\hline
Contrast & 3.2443 - 2.2905 & 5.1617 - 4.6504 \\
Correlation & 0.7869 - 0.8502 & 0.6967 - 0.7264 \\
Energy & 0.1608 - 0.1744 & 0.1106 - 0.1216 \\
Homogeneity & 0.6946 - 0.7462 & 0.6610 - 0.6995 \\
\end{tabular}
\end{center}
\end{table}

As shown in the Table \ref{tab:properties_differences}, small changes in the alignment of the print / scan can cause large variations in the properties values ​​obtained from the co-occurrence matrix.
